---
title: "Ontology Descent quickstart"
author: "Leonidas Lundell"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart of ontology descent method}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Quickstast for us. Will grow this into a proper vigete.

```{r}
# library(ontologyDescent)
library(igraph)
source("../R/clustering_functions.R")
# load(here::here("R/sysdata.rda"))#this doesnt pass the check.
load("../R/sysdata.rda")
```

The data in dataClustereR.Rdata (net especially), are generated using networkeR but take a while to generate. Just loading them here instead.

This is how you generate the network data.

```{r, results = FALSE, message = FALSE}
# net <- networkeR(ont = "MF")
```

Running clusterer. Outputs: igraph object, a result data.frame, and an list with community membership needed for internal stuff currently...

If you are running this with new data, make sure that every ontology term provided is found in the network as things are currently crashing.

```{r}
targets <- example_data$ontoID[1:50]
#filter out any terms not found in the network.
targets <- targets[targets %in% igraph::V(mf_hsa)$name]

results <- clustereR(ontoNet = mf_hsa, 
                     target = targets, 
                     filterTerms = c("RNA binding",
                                     "binding",
                                     "molecular_function",
                                     "protein binding"))
```

Plotting the network as well.

```{r, out.width="100%", dpi=300}
par(mar = c(0,0,0,0))
igraph::plot.igraph(results$plot,
     vertex.label = NA,
     vertex.label.cex = 0.5,
     vertex.border.cex = 0.000001,
     asp = 0,
     axes = F)

```

